### 2015-09-11 paper.tex
Add blank line
Clarify chord Reynolds number def

% For figure citations, please use "Fig." instead of "Figure".
A 1:6 scale model of the RM2 rotor was designed and built. Turbine geometric
parameters were scaled from the RM2 ``rev 0'' design report \cite{Barone2011},
with the exception of the shaft diameter, which was scaled from the SAFL RM2
shaft \cite{Hill2014}. The hubs were designed to be similar to the SAFL model,
which may aid in comparison of the results, though this was not a top priority.
Geometric parameters are shown in Tab.~\ref{tab:turb-geom} and a drawing of the
turbine design is shown in Fig.~\ref{fig:turbine-drawing}. The turbine model
components---blades, struts, shaft, and center hub sections---were fabricated
from 6061-T6 aluminum, which was hardcoat anodized per MIL-8625-A, type III,
class 2 specifications. CAD models of the turbine are available from
\cite{Bachant2015-RM2-CAD}.

@@

\begin{table}[ht]
\centering
\begin{tabular}{c|c|c|c|c}
Tow speed (m/s) & $Re_D$ & $Re_{c_\mathrm{tip}}$ & $Re_{c_\mathrm{root}}$ & $Re_{c_\mathrm{ave}}$\\ 
\hline 
0.4 & $4.3 \times 10^5$ & $5.0 \times 10^4$ & $8.3 \times 10^4$ & $6.6 \times 10^4$ \\ 
0.6 & $6.5 \times 10^5$ & $7.4 \times 10^4$ & $1.2 \times 10^5$ & $9.9 \times 10^4$ \\ 
0.8 & $8.6 \times 10^5$ & $9.9 \times 10^4$ & $1.7 \times 10^5$ & $1.3 \times 10^5$ \\ 
1.0 & $1.1 \times 10^6$ & $1.2 \times 10^5$ & $2.1 \times 10^5$ & $1.7 \times 10^5$ \\ 
1.2 & $1.3 \times 10^6$ & $1.5 \times 10^5$ & $2.5 \times 10^5$ & $2.0 \times 10^5$ \\ 
\end{tabular}

\caption{{\bf Test Reynolds numbers.} Turbine diameter and approximate blade
    chord Reynolds numbers $Re_c=\lambda U_\infty c / \nu$ corresponding to various
    tow speeds at $\lambda=3.1$.}

@@

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/perf_re_dep}
\caption{{\bf Reynolds Number effects on performance.}
Power and drag coefficient at $\lambda=3.1$ plotted versus Reynolds number.}
\label{fig:cp-re-dep}
\end{figure}

>>>>

% For figure citations, please use "Fig." instead of "Figure".

A 1:6 scale model of the RM2 rotor was designed and built. Turbine geometric
parameters were scaled from the RM2 ``rev 0'' design report \cite{Barone2011},
with the exception of the shaft diameter, which was scaled from the SAFL RM2
shaft \cite{Hill2014}. The hubs were designed to be similar to the SAFL model,
which may aid in comparison of the results, though this was not a top priority.
Geometric parameters are shown in Tab.~\ref{tab:turb-geom} and a drawing of the
turbine design is shown in Fig.~\ref{fig:turbine-drawing}. The turbine model
components---blades, struts, shaft, and center hub sections---were fabricated
from 6061-T6 aluminum, which was hardcoat anodized per MIL-8625-A, type III,
class 2 specifications. CAD models of the turbine are available from
\cite{Bachant2015-RM2-CAD}.

@@

\begin{table}[ht]
\centering
\begin{tabular}{c|c|c|c|c}
Tow speed (m/s) & $Re_D$ & $Re_{c_\mathrm{tip}}$ & $Re_{c_\mathrm{root}}$ & $Re_{c_\mathrm{mid}}$\\ 
\hline 
0.4 & $4.3 \times 10^5$ & $5.0 \times 10^4$ & $8.3 \times 10^4$ & $6.6 \times 10^4$ \\ 
0.6 & $6.5 \times 10^5$ & $7.4 \times 10^4$ & $1.2 \times 10^5$ & $9.9 \times 10^4$ \\ 
0.8 & $8.6 \times 10^5$ & $9.9 \times 10^4$ & $1.7 \times 10^5$ & $1.3 \times 10^5$ \\ 
1.0 & $1.1 \times 10^6$ & $1.2 \times 10^5$ & $2.1 \times 10^5$ & $1.7 \times 10^5$ \\ 
1.2 & $1.3 \times 10^6$ & $1.5 \times 10^5$ & $2.5 \times 10^5$ & $2.0 \times 10^5$ \\ 
\end{tabular}

\caption{{\bf Test Reynolds numbers.} Turbine diameter and approximate average
    blade chord Reynolds numbers $Re_c=\lambda U_\infty c / \nu$ at tip, root, and
    mid-span, corresponding to various tow speeds at $\lambda=3.1$.}

@@

\begin{figure}[h]
    \includegraphics[width=\textwidth]{figures/perf_re_dep}

    \caption{{\bf Reynolds Number effects on performance.} Power and drag
        coefficient at $\lambda=3.1$ plotted versus turbine diameter and approximate
        average blade root chord Reynolds number.}

    \label{fig:cp-re-dep}
\end{figure}
